---
title: "Bed Nets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bed Nets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(ramp.xds)
library(ramp.control)
```

```{r, echo=F}
#devtools::load_all()
```

Every bed net model has six configurable functions, each one dispatched and configured by a different object. 

***

The `bednets` model object: 

`bednets`

+ `$distribute_mod` 

+ `$owner_mod` 

+ `$user_mod` 

+ `$effects_mod` 

+ `$coverage_mod` 

+ **coverage** 

+ `$ef_sz_mod` 

    - [[1]] - for species 1 
    
    - ... 
    
***

The models get called at two different points:  

- `VectorControl` dispatches on `class(model$vector_control) == "dynamic"` 

    - `BedNet` dispatches on `class(model$bednets) == "dynamic"` 
    
        -  `DistributeBedNets` dispatches on `class(model$bednets$distribute_mod)` is there to model mass distribution of ITNs that should sharply increase bednet ownership 
        
        -  `OwnBedNets` dispatches on `class(model$bednets$owner_mod)` is a model that can account for background net replacement and loss 
        
        -  `UseBedNets` dispatches on  `class(model$bednets$user_mod)` is a model for bed net usage 
        
        -  `BedNetEffects` dispatches on  `class(model$bednets$effects_mod)` is a function that modifies search weights
        
- `VectorControlEffectSizes` dispatches on `class(model$bednets) == "dynamic"` 

    - `BedNetCoverage` dispatches on `class(model$bednets$coverage_mod)` 
    
    - After evaluating `BedNetCoverage`, values are stored at `model$bednets$coverage` 
    
    - `BedNetEffectSizes` dispatches on `class(model$bednets$ef_sz_mod[[s]])` for the $s^{th}$ species 

To set all this up, we call a function with a name that calls a setup function and as set of options to set it up, passed as a list:

```
setup_bednets = function(..., 
                        distribute_name = 'none', distribute_opts = list(),
                        own_name = 'none', own_opts = list(),
                        use_name = 'none', use_opts = list(),
                        effects_name = 'none', effects_opts = list(),
                        coverage_name = 'none', coverage_opts = list(),
                        effect_sizes_name = 'none', effect_sizes_opts = list(), 
                        ...
```

## Coverage 

In the simplest models, we can simply set coverage 

```{r}
mod <- xds_setup(MYZname = "SI")
```

```{r}
cov_opts <- list(
  F_season = function(t)
    {ifelse(t < 0, 0, (sin(2*pi*(t-365/4) / 365) + 1))}
)
```

```{r}
tt = seq(0:730)
with(cov_opts, plot(tt, F_season(tt), type = "l"))
```


```{r}
mod <- setup_bednets(mod,
     coverage_name = "func", coverage_opts = cov_opts, 
     effect_sizes_name = "lemenach")

tt = seq(0:730)
with(mod$bednets$coverage_mod, plot(tt, F_season(tt), type = "l"))
```

## Effect Sizes 

