---
title: "Mass Treatment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mass Treatment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(ramp.xds)
library(ramp.control)
```

**`ramp.control`** has utilities to set up and simulate mass treatment, including: 

+ mass drug administration (MDA) 
+ mass screen and treat (MSAT)  

In the following, we demonstrate how, and then we discuss the implementation. 


## Basic Setup 

The first step is basic setup. Before setting up MDA, it's a good idea to check that module is capable of handling mass treatment. To see if a module supports it, look at the skill set. For example, we can check whether the `SIS` supports MDA or MSAT. 

```{r}
skill_set_XH("SIS")$mda
```

The `SIS` module supports MDA. 

The next step is basic setup: 

```{r}
base_model <- xds_setup_eir(Xname = "SIS", 
                       eir=1/365, 
                       season_par = makepar_F_sin(phase=120))
```

Next we solve it. 

```{r, fig.height=4, fig.width=7}
base_model <- burnin(base_model) 
base_model <- xds_solve(base_model, 1095,5)
xds_plot_PR(base_model)
```

## Mass Treatment Events 

Adding mass treatment is an *advanced setup option.* The function call is **`setup_mass_treat_events`.** To use it, we need to pass:

+ `start` -- the julian date(s) 

+ `span` -- the length of the event

+ `frac_treated` -- the fraction that will be treated

+ `test` -- whether testing is done

    - `test=TRUE` configures MSAT 
    
    - `test=FALSE` configures MDA 

This sets up two rounds of MDA starting on days 180 and 480.  Each round lasts 10 days, and treats 90% of the population.  

```{r}
start = c(180, 480)
span = c(10,10)
frac_treated = c(0.9, 0.9)
test = c(FALSE, FALSE) 
mda_model <- setup_mass_treat_events(base_model, start, span, frac_treated, test)
```

Now we solve the base_model with MDA and compare it to the baseline:

```{r, fig.height=4, fig.width=7}
mda_model <- xds_solve(mda_model, 1095,5)
xds_plot_PR(base_model)
xds_plot_PR(mda_model, add=T, clrs = "darkred")
```

## Add Events 

To add another round of mass treatment, use **`add_mass_treat_events`.** This adds an extra round on day 600 that is like the others 2 rounds. 

```{r, fig.height=4, fig.width=7}
tt <- seq(0, 1095, by = 1)
mda_model_1 <- add_mass_treat_events(mda_model, 600, 10, .9, FALSE)
mda_model_1 <- xds_solve(mda_model_1, 1095,5)
show_mda(tt, mda_model_1)
```

If no mass treatment events have been set up, the function calls `setup_mass_treat_events.` This adds a mass treatment event to the `base_model`

```{r, fig.height=4, fig.width=7}
mda_model_2 <- add_mass_treat_events(base_model, 600, 10, .9, FALSE)
mda_model_2 <- xds_solve(mda_model_2, 1095,5)
show_mda(tt, mda_model_2)
```

This plot compares all four models:

```{r, fig.height=4, fig.width=7}
xds_plot_PR(mda_model_2, clrs="darkblue")
xds_plot_PR(mda_model_1, add=T, clrs = "purple3")
xds_plot_PR(base_model, add=T)
xds_plot_PR(mda_model, add=T, clrs = "darkred")
```

## Notes 

Treatment during the span of an event occurs at a fixed rate. The shape of the treatment curve is a variant of a `sharkfin` function:

```{r, fig.height=4, fig.width=7}
tt <- seq(598, 612, by = .1)
show_mda(tt, mda_model_1)
```

The total area under the curve is calibrated to reach the right fraction treated: in this case, 90%. We can check this:

```{r}
mda <- mda_model_1$mass_treat_obj$mda_obj$F_treat
t_frac = 1-exp(-integrate(mda, 595, 615)$val)
approx_equal(.9, t_frac, tol = 1e-6) 
```

